Response to reviewers

### 2025-01-24 Manuscript/ecography_reponse_letter_2.tex
Update ecography_reponse_letter_2.tex

\textit{(or, inversely, observations are more likely to be ``preserved''/``surviving'' in less dense regions)}. Lines @@@

@@

\textit{Note also that, as mentioned above, different dimensionalities can have different effects on the metrics, depending on both the traitspace and the metric nature (Bellman et al., 1957).} Lines388-390. %@@@

@@

We've now added the the glossary table (supplementary table 1) to the main text as suggested with the definition of trait redefined as a characteristic (good catch!).
We did however keep our broader definition of a trait as opposed to \cite{violle2007let}'s (see response to first comment of Reviewer 3 above).
We have added this precision in the table:

>>>>

\textit{(or, inversely, observations are more likely to be ``preserved''/``surviving'' in less dense regions)}. Lines 208-209. %@@@

@@

\textit{Note also that, as mentioned above, different dimensionalities can have different effects on the metrics, depending on both the traitspace and the metric nature (Bellman et al., 1957).} Lines 388-390. %@@@

@@

We've now added the the glossary table (supplementary table 1) to the main text as suggested with the definition of trait redefined as a characteristic (good catch!).
We did however keep our broader definition of a trait as opposed to Violle et al (2007)'s (see response to first comment of Reviewer 3 above).
We have added this precision in the table:
